---
title: "Package: normdrawandfill"
author: "Sulekha Aloorravi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

"normdrawandfill" is a package with function "normdrawandfill" to draw Normal distribution density curve (bell curve) and highlight different areas of distribution by filling the area with chosen color and displaying Probability percentages.

## **Function: normdrawandfill {normdrawandfill}**
## **Usage**
```{r, fig.show='hold', eval=FALSE}
normdrawandfill(mean=0,sd=1,points=200,linecolor="orange",fillcolor = "blue",fillafter = NULL,
fillbefore = NULL, fillwithin = NULL,thickness=40, xlabel = NULL, ylabel = NULL, axiscol = "red")
```

## **Arguments**
mean -   mean value of data  

sd -  standard deviation value of data

points - default value is 200. Changing this value will change the length of x-axis

linecolor -  line color of normal curve

fillcolor - color of the shaded area

fillafter - area after this x coordinate will be shaded

fillbefore - area before this x coordinate will be shaded

fillwithin - c(x1,x2) area within these two x coordinates will be shaded

thickness - integer value defining the density of shaded area

xlabel - Label for the x-axis

ylabel - Label for the y-axis

axiscol - color to highlight distance between mean and standard deviation in x-axis

## **Examples**
```{r eval=FALSE}
#Normal Distribution Curve
normdrawandfill(20000,5102,linecolor = "blue", xlab = "Quantity", ylab = "Probability Density")

#P(10000<X<30000)
normdrawandfill(20000,5102,linecolor = "red", xlab = "Quantity", ylab = "Probability Density",fillwithin = c(10000,30000), fillcolor = "cyan", thickness = 100)
d1 = paste("  P(10000<X<30000)=", "95%")
text(30000,0.00006,d1, font = 2, cex = 0.8)

#P(X<10000)
normdrawandfill(20000,5102,linecolor = "blue", xlab = "Quantity", ylab = "Probability Density",fillbefore = 10000, fillcolor = "lightgreen")
d1 = paste("  P(X<10000)=", "0.025%")
text(8000,0.00006,d1, font = 2, cex = 0.8)

#P(X>30000)
normdrawandfill(20000,5102,linecolor = "blue", xlab = "Quantity", ylab = "Probability Density",fillafter = 30000, fillcolor = "red")
d1 = paste("  P(X>30000)=", "0.025%")
text(30000,0.00006,d1, font = 2, cex = 0.8)
```

